NoTitle

### 2017-05-22 SpringerLNCS/sections/Overview.tex
More overview text.

\begin{lstlisting}
interface Deck {
  void draw() { // draws a card from the Deck
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      ...
    }
  }
}

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(true);
    ...
  }
}
\end{lstlisting}
Note that both methods have \lstinline|void| return type (we will not formalize
\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw()| tries to get the cards as a stack, pops
out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw()|
creates a blank canvas using \lstinline|JFrame|. Now, a programmer is designing a
card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
deck using multiple inheritance:

\begin{lstlisting}
interface DrawableDeck extends Drawable, Deck {
  ...
} 
\end{lstlisting}
The point of using multiple inheritance is surely for composing the features of
components, achieving great code reuse. It is supported by many mainstream OO
languages. Nevertheless at this point, \lstinline|DrawableDeck| has to throw a compile
error, for the two \lstinline|draw()| methods cause a conflict, though accidentally.

@@

\begin{lstlisting}
void func(Drawable obj) {
  obj.draw();
}

DrawableDeck d = new DrawableDeck();
d.Drawable::draw();       // calling draw() in Drawable
((Drawable) d).draw(); // calling draw() in Drawable
func(d);                 // calling draw() in Drawable
\end{lstlisting}
Thus we have: \paragraph{VI. Static dispatch.} Static dispatch finds out and invokes the most specific method ``by need''.

On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
C++ has the flexibility for choosing either way of dispatch by the ``virtual'' keyword.
Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, here we redefine \lstinline|Deck| to support
both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:
\begin{lstlisting}
interface Deck {
  void draw() {...}
  void shuffleAndDraw() {
    shuffle();
    draw();
  }
  ...
}
\end{lstlisting}
\lstinline|shuffleAndDraw()| is a designed method that invokes \lstinline|draw()| in its definition. In principle, we want
that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw()|:
\begin{lstlisting}
interface LoggingDeck {
  void draw() { // overriding
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      println("The card is: " + card.toString());
      ...
    } else {
      println("Empty deck.");
    }
  }
}
\end{lstlisting}
Usually we want to reuse the code of \lstinline|shuffleAndDraw()| during inheritance, hence dynamic dispatch is necessary, otherwise
programmers have to override all the other methods that invoke \lstinline|draw()|. However, as seen before, dynamic dispatch can cause
ambiguity if we have:
\begin{lstlisting}
interface DrawableLoggingDeck extends Drawable, LoggingDeck {
  ...
}

DrawableLoggingDeck d = new DrawableLoggingDeck();
d.shuffleAndDraw(); // ambiguous draw()
\end{lstlisting}
Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity.

\subsection{Solution in \MIM: \dispatchnamecaptical}

>>>>

\vspace{3pt}\begin{lstlisting}
interface Deck {
  void draw() { // draws a card from the Deck
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      ...
    }
  }
}

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(true);
    ...
  }
}
\end{lstlisting}\vspace{3pt}
Note that both methods have \lstinline|void| return type (we will not formalize
\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw()| tries to get the cards as a stack, pops
out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw()|
creates a blank canvas using \lstinline|JFrame|. Now, a programmer is designing a
card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
deck using multiple inheritance:

\vspace{3pt}\begin{lstlisting}
interface DrawableDeck extends Drawable, Deck {
  ...
} 
\end{lstlisting}\vspace{3pt}
The point of using multiple inheritance is surely for composing the features of
components, achieving great code reuse. It is supported by many mainstream OO
languages. Nevertheless at this point, \lstinline|DrawableDeck| has to throw a compile
error, for the two \lstinline|draw()| methods cause a conflict, though accidentally.

@@

\vspace{3pt}\begin{lstlisting}
void func(Drawable obj) {
  obj.draw();
}

DrawableDeck d = new DrawableDeck();
d.Drawable::draw();       // calling draw() in Drawable
((Drawable) d).draw(); // calling draw() in Drawable
func(d);                 // calling draw() in Drawable
\end{lstlisting}\vspace{3pt}
Thus we have: \paragraph{VI. Static dispatch.} Static dispatch finds out and invokes the most specific method ``by need''.

On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
C++ has the flexibility for choosing either way of dispatch by the ``virtual'' keyword.
Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, here we redefine \lstinline|Deck| to support
both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:
\vspace{3pt}\begin{lstlisting}
interface Deck {
  void draw() {...}
  void shuffleAndDraw() {
    shuffle();
    draw();
  }
  ...
}
\end{lstlisting}\vspace{3pt}
\lstinline|shuffleAndDraw()| is a representative method that invokes \lstinline|draw()| in its definition. In principle, we want
that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw()|:
\vspace{3pt}\begin{lstlisting}
interface LoggingDeck {
  void draw() { // overriding
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      println("The card is: " + card.toString());
      ...
    } else {
      println("Empty deck.");
    }
  }
}
\end{lstlisting}\vspace{3pt}
Usually we want to reuse the code of \lstinline|shuffleAndDraw()| during inheritance, hence dynamic dispatch is necessary, otherwise
programmers have to override all the other methods that invoke \lstinline|draw()|. However, as seen before, dynamic dispatch can cause
ambiguity if we have:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck extends Drawable, LoggingDeck {
  ...
}

DrawableLoggingDeck d = new DrawableLoggingDeck();
d.shuffleAndDraw(); // ambiguous draw()
\end{lstlisting}\vspace{3pt}
Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity. Therefore, we need to find another algorithm for method binding.

\subsection{Solution in \MIM: \dispatchnamecaptical}
Our \MIM{} model uses \dispatchnameit{} for method lookup. A qualified method invocation, for instance, \lstinline|e.I::m()|, is read as ``finding the most specific \lstinline|m()| along path \lstinline|I|''. The meaning of ``along path \lstinline|I|'' is that, if the result of \dispatch{} is \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type, and \lstinline|J| has a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|). Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an overridden version after \lstinline|I| like dynamic dispatch. The formal definition will be introduced later.

In the above example, when

Now we can actually redefine \lstinline|Deck| as follows:
\vspace{3pt}\begin{lstlisting}
interface Deck {
  void draw() {...}
  void shuffleAndDraw() {
    this.Deck::shuffle();
    this.Deck::draw();
  }
  ...
}
\end{lstlisting}\vspace{3pt}
It guarantees that \lstinline|shuffleAndDraw()| are calling \lstinline|shuffle()| and \lstinline|draw()| from its own branch, so that the namesakes
from other branches will not cause conflicts. Now \lstinline|d.shuffleAndDraw()| is no longer ambiguous.

The above example reflects the general case, that is, all method calls with receiver ``\lstinline|this|'' need to be qualified with its enclosing interface name, so as to avoid potential conflicts. Actually in \MIM{}, we can still write ``\lstinline|shuffle();|'' and ``\lstinline|draw();|''
in \lstinline|Deck|, because \MIM{} automatically desugars those method calls to qualified ones, by its implicit semantic rules.
\textcolor{red}{Haoyuan: More. super call. update.}
